RDF Constraints to Validate

### 2015-04-29 paper/paper7/paper7-appendix.tex
Revert "Language Improvement in Paper 2"
This reverts commit 970632ac38c80aacbc178530c32b0c1e1a48fbad.

Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}. 
It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.

@@

The following two sections encompass RDF constraints classified as constraint types either corresponding to RDF validation requirements (section \ref{RDF-validation-requirements-constraint-types}) or data model specific constraint types (section \ref{data-model-specific-constraint-types}).
Constraint types marked with an asterisk (*) can be used as OWL 2 axioms. Thus, reasoners may be used prior to the validation to infer implicit triples which may resolve or cause constraint violations.
$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}.
As $\mathcal{C}_{T}$ and $\mathcal{C}_{C}$ are disjoint sets, $\mathcal{C}_{C}$ constraint types are not explicitly marked.

@@

\subsection{Subsumption*\textsuperscript{T}}

@@

\subsection{Class Equivalence*\textsuperscript{T}}

@@

\subsection{Sub Properties*\textsuperscript{T}}

@@

\subsection{Property Domains*\textsuperscript{T}}

@@

\subsection{Property Ranges*\textsuperscript{T}}

@@

\subsection{Inverse Object Properties*}

@@

\subsection{Symmetric Object Properties*}

@@

\subsection{Asymmetric Object Properties*\textsuperscript{T}}

@@

\subsection{Reflexive Object Properties*}

@@

\subsection{Irreflexive Object Properties*}

@@

\subsection{Class-Specific Irreflexive Object Properties*}

@@

\subsection{Disjoint Properties\textsuperscript{T}}

@@

\subsection{Disjoint Classes\textsuperscript{T}}

@@

\subsection{Context-Specific Property Groups}

@@

\subsection{Context-Specific Inclusive OR of Properties}

@@

\subsection{Context-Specific Inclusive OR of Property Groups}

@@

\subsection{Recursive Queries}

@@

\subsection{Individual Inequality}

@@

\subsection{Equivalent Properties*\textsuperscript{T}}

@@

\subsection{Property Assertions}

@@

\subsection{Data Property Facets}

@@

\subsection{Literal Pattern Matching}

@@

\subsection{Negative Literal Pattern Matching}

@@

\subsection{Object Property Paths*}

@@

\subsection{Intersection*}

@@

\subsection{Disjunction*}

@@

\subsection{Negation*}

@@

\subsection{Existential Quantifications*\textsuperscript{T}}

@@

\subsection{Universal Quantifications*\textsuperscript{T}}

@@

\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{T}}

@@

\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{T}}

@@

\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{T}}

@@

\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{T}}

@@

\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{T}}

@@

\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{T}}

@@

\subsection{Transitive Object Properties*}

@@

\subsection{Context-Specific Exclusive OR of Properties}

@@

\subsection{Context-Specific Exclusive OR of Property Groups}

@@

\subsection{Allowed Values\textsuperscript{T}}

@@

\subsection{Not Allowed Values}

@@

\subsection{Literal Ranges}

@@

\subsection{Negative Literal Ranges}

@@

\subsection{Required Properties\textsuperscript{T}}

@@

\subsection{Optional Properties\textsuperscript{T}}

@@

\subsection{Repeatable Properties\textsuperscript{T}}

@@

\subsection{Negative Property Constraints}

@@

\subsection{Individual Equality*}

@@

\subsection{Functional Properties*}

@@

\subsection{Inverse-Functional Properties*}

@@

\subsection{Value Restrictions*}

@@

\subsection{Self Restrictions*}

@@

\subsection{Primary Key Properties}

@@

\subsection{Class-Specific Property Range*\textsuperscript{T}}

@@

\subsection{Class-Specific Reflexive Object Properties*}

@@

\subsection{Membership in Controlled Vocabularies.}

@@

\subsection{IRI Pattern Matching}

@@

\subsection{Literal Value Comparison}

@@

\subsection{Ordering}

@@

\subsection{Validation Levels}

@@

\subsection{String Operations}

@@

\subsection{Context-Specific Valid Classes\textsuperscript{T}}

@@

\subsection{Context-Specific Valid Properties\textsuperscript{T}}

@@

\subsection{Default Values*\textsuperscript{T}}

@@

\subsection{Mathematical Operations}

@@

\subsection{Language Tag Matching}

@@

\subsection{Language Tag Cardinality}

@@

\subsection{Whitespace Handling}

@@

\subsection{HTML Handling}

@@

\subsection{Conditional Properties}

@@

\subsection{Recommended Properties}

@@

\subsection{Handle RDF Collections}

@@

\subsection{Value is Valid for Datatype\textsuperscript{T}}

@@

\subsection{Use Sub-Super Relations in Validation\textsuperscript{T}}

@@

\subsection{Cardinality Shortcuts*\textsuperscript{T}}

@@

\subsection{Aggregation}

@@

\subsection{Provenance}

@@

\subsection{Comparison}

@@

\subsection{Data Model Consistency}
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

@@

\subsection{Structure}

@@

\subsection{Labeling and Documentation}

@@

\subsection{Vocabulary\textsuperscript{T}}
Vocabularies should not invent any new terms or use deprecated elements.

@@

\subsection{Linked Data}

>>>>

Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}. 
It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
Bosch et al. identified in total 76 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.

@@

The following two sections encompass RDF constraints classified as constraint types either corresponding to RDF validation requirements (section \ref{RDF-validation-requirements-constraint-types}) or data model specific constraint types (section \ref{data-model-specific-constraint-types}).
Constraint types marked with an asterisk (*) can be used as OWL 2 axioms. Thus, reasoners may be used prior to the validation to infer implicit triples which may resolve or cause constraint violations.
$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{B}.
As $\mathcal{C}_{T}$ and $\mathcal{C}_{C}$ are disjoint sets, $\mathcal{C}_{C}$ constraint types are not explicitly marked.

@@

\subsection{Subsumption*\textsuperscript{B}}

@@

\subsection{Class Equivalence*\textsuperscript{B}}

@@

\subsection{Sub Properties*\textsuperscript{B}}

@@

\subsection{Property Domains*\textsuperscript{B}}

@@

\subsection{Property Ranges*\textsuperscript{B}}

@@

\subsection{Inverse Object Properties*\textsuperscript{B}}

@@

\subsection{Symmetric Object Properties*\textsuperscript{B}}

@@

\subsection{Asymmetric Object Properties*\textsuperscript{B}}

@@

\subsection{Reflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Irreflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Class-Specific Irreflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Disjoint Properties\textsuperscript{B}}

@@

\subsection{Disjoint Classes\textsuperscript{B}}

@@

\subsection{Context-Specific Property Groups\textsuperscript{C}}

@@

\subsection{Context-Specific Inclusive OR of Properties\textsuperscript{C}}

@@

\subsection{Context-Specific Inclusive OR of Property Groups\textsuperscript{C}}

@@

\subsection{Recursive Queries\textsuperscript{C}}

@@

\subsection{Individual Inequality\textsuperscript{B}}

@@

\subsection{Equivalent Properties*\textsuperscript{B}}

@@

\subsection{Property Assertions\textsuperscript{B}}

@@

\subsection{Data Property Facets\textsuperscript{S}}

@@

\subsection{Literal Pattern Matching\textsuperscript{S}}

@@

\subsection{Negative Literal Pattern Matching\textsuperscript{S}}

@@

\subsection{Object Property Paths*\textsuperscript{B}}

@@

\subsection{Intersection*\textsuperscript{B}}

@@

\subsection{Disjunction*\textsuperscript{B}}

@@

\subsection{Negation*\textsuperscript{B}}

@@

\subsection{Existential Quantifications*\textsuperscript{B}}

@@

\subsection{Universal Quantifications*\textsuperscript{B}}

@@

\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Transitive Object Properties*\textsuperscript{B}}

@@

\subsection{Context-Specific Exclusive OR of Properties\textsuperscript{C}}

@@

\subsection{Context-Specific Exclusive OR of Property Groups\textsuperscript{C}}

@@

\subsection{Allowed Values\textsuperscript{B}}

@@

\subsection{Not Allowed Values\textsuperscript{B}}

@@

\subsection{Literal Ranges\textsuperscript{S}}

@@

\subsection{Negative Literal Ranges\textsuperscript{S}}

@@

\subsection{Required Properties\textsuperscript{B}}

@@

\subsection{Optional Properties\textsuperscript{B}}

@@

\subsection{Repeatable Properties\textsuperscript{B}}

@@

\subsection{Negative Property Constraints\textsuperscript{S}}

@@

\subsection{Individual Equality*\textsuperscript{B}}

@@

\subsection{Functional Properties*\textsuperscript{B}}

@@

\subsection{Inverse-Functional Properties*\textsuperscript{B}}

@@

\subsection{Value Restrictions*\textsuperscript{B}}

@@

\subsection{Self Restrictions*\textsuperscript{B}}

@@

\subsection{Primary Key Properties*\textsuperscript{B}}

@@

\subsection{Class-Specific Property Range*\textsuperscript{B}}

@@

\subsection{Class-Specific Reflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Membership in Controlled Vocabularies\textsuperscript{S}}

@@

\subsection{IRI Pattern Matching\textsuperscript{S}}

@@

\subsection{Literal Value Comparison\textsuperscript{S}}

@@

\subsection{Ordering\textsuperscript{C}}

@@

\subsection{Validation Levels\textsuperscript{S}}

@@

\subsection{String Operations\textsuperscript{S}}

@@

\subsection{Context-Specific Valid Classes\textsuperscript{B}}

@@

\subsection{Context-Specific Valid Properties\textsuperscript{B}}

@@

\subsection{Default Values*\textsuperscript{S}}

@@

\subsection{Mathematical Operations\textsuperscript{C}}

@@

\subsection{Language Tag Matching\textsuperscript{S}}

@@

\subsection{Language Tag Cardinality\textsuperscript{S}}

@@

\subsection{Whitespace Handling\textsuperscript{S}}

@@

\subsection{HTML Handling\textsuperscript{S}}

@@

\subsection{Conditional Properties\textsuperscript{C}}

@@

\subsection{Recommended Properties\textsuperscript{S}}

@@

\subsection{Handle RDF Collections\textsuperscript{C}}

@@

\subsection{Value is Valid for Datatype\textsuperscript{B}}

@@

\subsection{Use Sub-Super Relations in Validation\textsuperscript{B}}

@@

\subsection{Cardinality Shortcuts*\textsuperscript{B}}

@@

\subsection{Aggregation\textsuperscript{C}}

@@

\subsection{Provenance\textsuperscript{S}}

@@

\subsection{Comparison\textsuperscript{C}}

@@

\subsection{Data Model Consistency\textsuperscript{C}}
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

@@

\subsection{Structure\textsuperscript{C}}

@@

\subsection{Labeling and Documentation\textsuperscript{S}}

@@

\subsection{Vocabulary\textsuperscript{B}}
Vocabularies should not invent any new terms or use deprecated elements.

@@

\subsection{HTTP URI Scheme Violation\textsuperscript{S}}
